Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2021-08-26 inst/surfing_jsa.tex
better title
keywords

  \title{Analysis of competitive surfing tournaments with generalized Bradley-Terry}

@@

\subsubsection*{Abstract}
Here we analyse competitive surfing, specifically the 2019 World Surf
League, using formal statistical methods.  We use generalized
Bradley-Terry likelihoods to assess a number of hypotheses of interest
to the surfing community.  Specifically, we quantify the dominance of
the top competitors using likelihood techniques, and go on to study
the ``Brazilian storm'' phenomenon using reified entities in two ways.
Firstly we assess the supposed Brazilian preference for beach break
and point break wave types; and secondly we consider results from the
perspective of tournament theory and test for competitors modifying
their strategy in the presence of compatriot rivals.  We quantify the
evidence for these commonly assumed features of contemporary
competitive surfing and suggest further avenues of research.
\newpage

>>>>

  \title{Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods}

@@

\subsubsection*{Abstract}
Here we analyse competitive surfing, specifically the 2019 World Surf
League, using formal statistical methods.  We use generalized
Bradley-Terry likelihoods to assess a number of hypotheses of interest
to the surfing community.  Specifically, we quantify the dominance of
the top competitors using likelihood techniques, and go on to study
the ``Brazilian storm'' phenomenon using reified entities in two ways.
Firstly we assess the supposed Brazilian preference for beach break
and point break wave types; and secondly we consider results from the
perspective of tournament theory and test for competitors modifying
their strategy in the presence of compatriot rivals.  We quantify the
evidence for these commonly assumed features of contemporary
competitive surfing and suggest further avenues of research.

keywords: Reified Bradley-Terry, surfing, competitive surfing, noncompetitive behaviour, likelihood methods, Brazilian storm
\newpage
